Presentation Title

### 2017-08-02 thesis/chapters/ch2-problem.tex
Write conclusion and fix references
Refactor validation protocol

The decentralised and democratic nature of blockchain technology removes central point of control or failure.
However, as we described in the Introduction, it faces a genuine scalability problem.
In particular, proof-of-work based systems are unlikely to reach a transaction rate suitable for ubiquitous use, even with parameter tuning.
What we wish to see is horizontal scalability.
That is, by adding new nodes into the network, the global transaction rate should increase proportionally.
Hence, the research question we answer in this  work is the following.
\begin{displayquote}
\emph{How do we design a blockchain consensus protocol that is fault tolerant, scalable and can reach global consensus?}
\end{displayquote}

@@

\section{Global consensus}

@@

\section{Security and fault tolerance}

@@

\section{Performance and scalability}

@@

\section{Limitations}
Our work aims to significantly lower the transaction bound.
However, the price to pay is that the Sybil attack~\cite{douceur2002sybil} prevention mechanism moves from the blockchain consensus protocol to the application layer.
For example, social network based Sybil defence mechanims use graph structure of real-world relationships~\cite{yu2006sybilguard}.
Online marketplaces such as Amazon use the rating of buyer and sellers.
Since our system is application neutral, we do not provide an explicit Sybil defence mechanism.
On the other hand, our system also has no restrictions on the Sybil defence technique
and applications built on top of our system can use the best mechanism for their purpose.

>>>>

From the Introduction, we saw that early blockchain systems face a scalability problem.
In particular, proof-of-work based systems are unlikely to reach a transaction rate suitable for ubiquitous use.
Many attempts to fix the scalability problem exist in academia as well as the industry.
In this chapter we describe the related work in the form of a mini taxonomy and identify areas for improvement and limitations.
Then we state our research question which

\section{Related work and mini taxonomy}

\section{Research question}

% TODO fix
What we wish to see is horizontal scalability.
That is, by adding new nodes into the network, the global transaction rate should increase proportionally.
Hence, the research question we answer in this  work is the following.
\begin{displayquote}
\emph{Is it possible to design a blockchain consensus protocol that is fault tolerant, scalable and can reach global consensus?}
\end{displayquote}

@@

\subsection{Global consensus}

@@

\subsection{Security and fault tolerance}

@@

\subsection{Performance and scalability}

@@

\subsection{Limitations}
Our work aims to significantly lower the transaction bound.
However, the price to pay is that the Sybil attack~\cite{douceur2002sybil} prevention mechanism moves from the blockchain consensus protocol to the application layer.
For example, social network based Sybil defence mechanims use graph structure of real-world relationships~\cite{yu2006sybilguard}.
Online marketplaces such as Amazon use the rating of buyer and sellers.
Since our system is application neutral, we do not provide an explicit Sybil defence mechanism.
On the other hand, our system also has no restrictions on the Sybil defence technique
and applications built on top of our system can use the best mechanism for their purpose.

### 2017-08-02 thesis/chapters/ch3-model.tex
Refactor validation protocol

\subsection{Validity definition}
A transaction can be in one of three states in terms of validity---\emph{valid}, \emph{invalid} and \emph{unknown}.
Given a fragment $F_{v, j}$, the validity of the transaction $t_{u, i}$ is captured by the function $\textsf{get\_validity}(t, F)$ (\Cref{alg:get-validity}).
The first four conditions (up to \Cref{line:valid-fragment}) essentially check whether the fragment is the one that the verifier needs.
If it is not, then the verifier cannot make any decision and return \emph{unknown}.
This is likely to be the case for new transactions because $\textsf{agreed\_fragment}(\cdot)$ would be $\bot$.
The next two conditions check for tampering or missing blocks, if any of these misconducts are detected, then the TX is invalid.

@@

Further, the caller of $\textsf{get\_validity}(t_{u, i}, F_{v, i})$ is not necessarily 
$u$\footnote{In practice it often is because after completing the TX protocol the parties are incentivised to check that the counterparty ``did the right thing''.}
Any node $w$ may call $\textsf{get\_validity}(t_u{u, i}, F_{v, i})$ as long as the caller $w$ has an agreed fragment of $t_{u, i}$---$F_{u, i}$.
$F_{u, i}$ may be readily available if $w = u$ or it may be from some other \texttt{vd\_resp} message, which we describe next in the validation protocol.

\begin{algorithm}
\caption{Function $\textsf{get\_validity}(t_{u, i}, F_{v, j})$ validates the transaction $t_{u, i}$.
$F_{v, j}$ is the corresponding fragment received from $v$.}
We assume there exist a valid $F_{u, i}$, namely the agreed fragment of $t_{u, i}$. 
The caller is $w$, it may be $u$ but this is not necessary.
\label{alg:get-validity}

@@

    % \State $F_{u, i} \gets \textsf{agreed\_fragment}(t_{u, i})$
    % \If{$F_{u, i} = \bot$}
    %     \State \Return \emph{unknown}
    % \EndIf \Comment $u$ has agreed fragment
    % \State

    \State $c_{v, a} \gets \textsf{first}(F_{v, j})$
    \State $c_{v, b} \gets \textsf{last}(F_{v, j})$
    \If{$c_{v, a}$ or $c_{v, b}$ are not in consensus}
        \State \Return \emph{unknown}
    \EndIf
    \State \Comment $v$ has agreed fragment

    % \If{$|F_{v, j}| > L$}
    %     \State \Return \emph{unknown}
    % \EndIf \Comment fragment not too long
    % \State

    % txid are equal now, but bad hash pointer
    \If{sequence number in $F_{v, j}$ is correct (sequential)}
        \If{hash pointers in $F_{v, j}$ is wrong}
            \State \Return \emph{unknown}
        \EndIf
    \EndIf
    \State \Comment correct TrustChain structure

    \State $c_{u, b} \gets \textsf{last}(F_{u, i})$
    \If{$c_{u, b}$ is not created using the same $\C_r$ as $c_{v, b}$}
        \State \Return \emph{unknown}
    \EndIf
    \State \Comment correct consensus round
    \label{line:valid-fragment}
    \State $\langle \_, \_, txid, pk_v, m, \_ \rangle \gets t_{u, i}$
    \If{number of blocks of $txid$ in $F_{v, j} \ne 1$}
        \State \Return \emph{invalid}
    \EndIf
    \State \Comment TX exists

    \State $\langle \_, \_, txid', pk'_u, m', \_ \rangle \gets t_{v, j}$
    \If{$m \ne m' \vee pk_u \ne pk'_u$}
        \State \Return \emph{invalid}
    \EndIf
    \State \Comment no tampering
    \State \Return \emph{valid}
\end{algorithmic}
\end{algorithm}

@@

    \Upon $\langle \texttt{vd\_resp}, txid, F_{v, j} \rangle$ from $v$
        \State $t_{u, i} \gets \text{the transaction identified by } txid$
        \State set the validity of $t_{u, i}$ to $\textsf{get\_validity}(t_{u, i}, F_{v, j})$
\end{algorithmic}
\end{algorithm}

>>>>

\subsection{Validity definition}
A transaction can be in one of three states in terms of validity---\emph{valid}, \emph{invalid} and \emph{unknown}.
Given a fragment $F_{v, j}$, the validity of the transaction $t_{u, i}$ is captured by the function $\textsf{get\_validity}(t, F_u, F_v)$ (\Cref{alg:get-validity}).
The first four conditions (up to \Cref{line:valid-fragment}) essentially check whether the fragment is the one that the verifier needs.
If it is not, then the verifier cannot make any decision and return \emph{unknown}.
This is likely to be the case for new transactions because $\textsf{agreed\_fragment}(\cdot)$ would be $\bot$.
The next two conditions check for tampering or missing blocks, if any of these misconducts are detected, then the TX is invalid.

@@

Further, the caller of $\textsf{get\_validity}(t_{u, i}, F_{u, i}, F_{v, j})$ is not necessarily 
$u$\footnote{In practice it often is because after completing the TX protocol the parties are incentivised to check that the counterparty ``did the right thing''.}
Any node $w$ may call $\textsf{get\_validity}(t_u{u, i}, F_{u, i}, F_{v, j})$ as long as the caller $w$ has an agreed fragment of $t_{u, i}$---$F_{u, i}$.
$F_{u, i}$ may be readily available if $w = u$ or it may be from some other \texttt{vd\_resp} message, which we describe next in the validation protocol.

\begin{algorithm}
\caption{Function $\textsf{get\_validity}(t_{u, i}, F_{u, i}, F_{v, j})$ validates the transaction represented by $t_{u, i}$.
We assume $F_{u, i}$ is always correct and contains $t_{u, i}$.
$F_{v, j}$ is the corresponding fragment received from $v$.}
\label{alg:get-validity}

@@

    \If{$F_{v, j}$ is not a fragment created in the same round as $F_{u, i}$}
        \State \Return \emph{unknown}
    \EndIf
    \State

    \label{line:valid-fragment}
    \State $\langle \_, \_, txid, pk_v, m, \_ \rangle \gets t_{u, i}$
    \If{number of blocks of $txid$ in $F_{v, j} \ne 1$}
        \State \Return \emph{invalid}
    \EndIf
    \State

    \State $t_{v, j} \gets $ the TX block with $txid$ in $F_{v, j}$
    \State $\langle \_, \_, txid', pk_u, m', \_ \rangle \gets t_{v, j}$

    % message tampering
    \If{$m \ne m' $} 
        \State \Return \emph{invalid}
    \EndIf
    \State

    % signature tampering
    \If{$t_{u, i} \text{ is not signed by } pk_u \vee t_{v, j} \text{ is not signed by } pk_v $}
        \State \Return \emph{invalid}
    \EndIf
    \State \Return \emph{valid}
\end{algorithmic}
\end{algorithm}

@@

    \Upon $\langle \texttt{vd\_resp}, txid, F_{v, j} \rangle$ from $v$
        \State $t_{u, i} \gets \text{the transaction identified by } txid$
        \If{$F_{u, i}$ and $F_{v, j}$ are available and $F_{u, i}$ is the agreed fragment of $t_{u, i}$}
            \State set the validity of $t_{u, i}$ to $\textsf{get\_validity}(t_{u, i}, F_{u, j}, F_{v, j})$
        \EndIf
\end{algorithmic}
\end{algorithm}
